Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-02-04 paper.tex
various changes

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{listings}
\usepackage{times}
\usepackage{wrapfig}
\renewcommand{\floatpagefraction}{.8}

@@

\newcommand{\numAugraphyAugmentations}{\emph{26}}

@@

\begin{abstract}
This paper introduces Augraphy, a Python library for constructing data augmentation pipelines for producing common perturbations seen in real-world document image datasets.
Augraphy stands apart from other data augmentation tools by providing many different augmentation strategies to produce augmented versions of clean document images that appear as if they have been distorted from standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
We discuss the Augraphy tool, showing how it can be used both as a data augmentation tool for producing diverse training data for tasks such as document de-noising, as well as generating challenging test data for evaluating model robustness on document image modeling tasks.

@@

\section{Introduction}
Life in the modern world involves a plethora of tasks that require automated and intelligent solutions for handling unstructured data.
Often, this data is in the form of documents, which may appear very different from when they were originally produced, having been altered in the physical world by printing, scanning, or photocopying processes.
Such real-world phenomena may introduce many types of distortions: for instance, folds, wrinkles, or tears in a page can cause color changes and shadows in a scanned document image; low or high printer ink settings may cause some regions of a document to be lighter or darker; and human-made annotations like highlighting or pencil marks can add noise to the page.

Many machine learning operations involving documents are impacted by the presence of noise; high-level tasks like document classification and information extraction are often expected to perform well even on noisily-scanned document images.
For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
Other intermediate-level tasks like optical character recognition (OCR) and page layout analysis may perform optimally if noise in a document image is minimized \cite{character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.
Further, the lower-level task of document de-noising tackles the document noise problem more directly by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
Such tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation.

%\begin{figure} % temp placeholder for figure... this figure should be compelling and help the reader understand what Augraphy is about
%\centering
%\fbox{
%    \begin{minipage}{2in}
%        \hfill\vspace{1in}
%    \end{minipage}
%    }
%\caption{Placeholder for compelling figure to help the reader understand what Augraphy is about.}   
%\end{figure}

@@

For this reason we introduce \emph{Augraphy}, an open-source Python-based data augmentation library for generating versions of document images that contain realistic noise artefacts commonly introduced via scanning, photocopying, and other office room procedures.
\emph{Augraphy} differs from most image data augmentation tools by specifically targeting the types of alterations and degradations seen in document images.
\emph{Augraphy} offers \numAugraphyAugmentations ~individual augmentation methods out-of-the-box across three ``phases" of augmentations, and these individual phase augmentations can be composed together along with a where different paper backgrounds can be added to the augmented image.
The resulting document images are realistic, noisy versions of clean documents, as evidenced in Figure~\ref{fig:intro}, where we apply several \emph{Augraphy} augmentations to a clean document image in order to mimic the types of noise seen in a real-world noisy document image from RVL-CDIP.
This paper provides an overview of the \emph{Augraphy} library, and demonstrates how it can be used both as a training data augmentation tool and as an effective means for producing data for robustness testing.

\begin{table}[]
    \centering
    \caption{Comparison of various image-based data augmentation libraries. Number of augmentations is a rough count, and many augmentations in other tools are what Augraphy calls Utilities. Further, many single augmentations in Augraphy --- geometric transforms, for example --- are represented by multiple classes in other libraries.}
    \scalebox{0.9}{
    \begin{tabular}{lccccc}
    \toprule
        \textbf{Library} & \textbf{Num.} & \textbf{Document-} & \textbf{Pipeline-} & & \\
        \textbf{Name} & \textbf{Augmentations} & \textbf{Centric} & \textbf{Based} & \textbf{Python} & \textbf{License}  \\
    \midrule
        \emph{Augmentor} \cite{augmentor} & 27 & \xmark &  & \cmark & MIT \\
        \emph{Albumentations} \cite{ref_albumentations} & 216 & \xmark & \cmark & \cmark & MIT \\
        \emph{imgaug} \cite{ref_imgaug} & 168& \xmark & \cmark & \cmark & MIT \\
        \emph{Augly} \cite{Papakipos2022-gq-augly} & 34 & \xmark & & \cmark & MIT \\
        \emph{DocCreator} \cite{ref_DocCreator} & 12 & \cmark & \xmark & \xmark & LGPL-3.0 \\
        \emph{Augraphy} (ours) & \numAugraphyAugmentations & \cmark & \cmark & \cmark & MIT\\
    \bottomrule
    \end{tabular}}
    \label{tab:augmentation-library-comparison}
\end{table}

\section{Related Work}\label{sec:related-work}

%This section discusses prior work related to document data augmentation, robustness testing, and document de-noising.
This section discusses prior work related to data augmentation and robustness testing, especially as it relates to document understanding and processing tasks.

\subsection{Data Augmentation}
A wide variety of data augmentation tools and pipelines exist for machine learning tasks ranging from natural language processing (e.g., \cite{feng-etal-2021-survey,fadaee-etal-2017-data,wei-zou-2019-eda}), audio and speech processing (e.g., \cite{ko15_interspeech,audiogmenter,audio-framework}), and computer vision and image processing.
In the image realm of image processing and computer vision, data augmentation tools and pipelines include \emph{Augly} \cite{Papakipos2022-gq-augly}, \emph{Augmentor} \cite{augmentor}, \emph{Albumentations} \cite{ref_albumentations}, \emph{DocCreator} \cite{ref_DocCreator}, Pytorch \cite{pytorch}, and \emph{imgaug} \cite{ref_imgaug}.
Augmentation strategies from these image-centric libraries are typically general purpose, and include image transformations like rotations, warps, and color modifications.
Table~\ref{tab:augmentation-library-comparison} compares \emph{Augraphy} with other image-based data augmentation libraries and tools.
As can be seen, these other data augmentation libraries do not specifically provide support for imitating the corruptions commonly seen in document analysis corpora.

A notable exception to this is the \emph{DocCreator} image synthesizing tool \cite{ref_DocCreator}, which is targeted towards creating synthetic images that mimic common corruptions seen in document collections.
\emph{DocCreator} differs from \emph{Augraphy} in several ways, however.
The first difference is that \emph{DocCreator}'s augmentations are meant to imitate those seen in historical (e.g., ancient or medieval) documents, while \emph{Augraphy} is meant to replicate noise caused by noisy office room procedures.
\emph{DocCreator} is also written in the C++ programming language and is a monolithic what-you-see-is-what-you-get (WYSIWYG) tool, and does not have a scripting or API interface to enable use in a broader machine learning pipeline.
\emph{Augraphy}, in contrast, is written in Python and can be easily integrated into machine learning model development and evaluation pipelines, and can easily be used alongside other Python packages.

@@

The introduction of noise-like corruptions and other modifications to image data can be used as a way of estimating and evaluating model robustness.
Prior work in this space includes the use of image blurring, contrast and brightness changes, color alterations, partial occlusions, geometric transformations, pixel-level noise (e.g., salt-and-pepper noise, impulse noise, etc.), and compression artefacts (e.g., JPEG) to evaluate image classification and object detection models (e.g., \cite{image-quality-impact,imagenet-c,pathology-recommendations,Hosseini2017-kn-google-api,face-recognition-impact,pathology-schomig,Vasiljevic2016-al-bluring-impact}).
More specific to the document understanding field, recent prior work has used basic noise-like corruptions to evaluate the robustness of document classifiers trained on RVL-CDIP \cite{saifullah-2022}.
Our paper also uses robustness testing as a way to showcase the effectiveness of \emph{Augraphy}, but rather than general image modifications like those described above, we use document-centric modifications.

%\section{Document Distortion, Theory \& Technique}
%Many approaches exist for adding features to an image, and many types of feature can be generated. The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.\\
%
%These types of feature are certainly useful in general image analysis and understanding, but bear little relation to the types of features commonly found in real-world documents. A sheet of paper out in the world begins its life as wood pulp, bleached, drained, and pressed flat by a long series of rollers. These are cut to size and stacked, then bound in reams and sent out for sale and use. This is the last time the sheet is clean in its useful lifetime, and even at this point, manufacturing defects can lead to variations in the paper, even between two pages in the same ream. At the point of use, these pages are loaded into a printer where they are stamped or dusted in toner and burned with lasers or sprayed with ink. Any of these processes may alter the local texture or global topology of the sheet. The pages may receive handwritten marks at any point before or after printing, and may subsequently be folded, creased, crumpled, flattened, burned, stained, soaked, or generally be subject to any of a million other operations. Any secretary can describe hundreds of different document distortion features; any schoolteacher, thousands.\\
%
%Augraphy's suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle. Every feature just listed has either a direct implementation already within the library or on the development roadmap, with more planned.\\
%
%Some techniques exist for introducing these features into images of documents, including but not limited to the following:
%\begin{enumerate}
%\item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used. The NoisyOffice team did this.
%\item Similarly, any markup features may be generated and overlaid by the same methods.
%\item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
%\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator has a function to do this.
%\end{enumerate}
%
%Augraphy already has a story for the first three, with the fourth in planning.

\section{Augraphy}
This section dives into detail about the \emph{Augraphy} library.
We first provide a high-level motivation for and overview of the library, then discuss the various augmentations supported out-of-the-box, and finally discuss details of the structure of the library.

\subsection{Motivation}

As mentioned in Section~\ref{sec:related-work}, several libraries and tools exist for augmenting image data.
These approaches alter images by adding Gaussian noise, applying blurring filters, and using geometric transformations like scaling, rotating, translating, cropping, downsampling, and so on.
While these types of modifications are useful in general image applications, they bear little relation to the types of features comonly found in real-world document image datasets.

A sheet of paper out in the world begins its life as wood pulp, bleached, drained, and pressed flat by a long series of rollers.
These are cut to size and stacked, then bound in reams and sent out for sale and use.
This is the last time the sheet is clean in its useful lifetime, and even at this point, manufacturing defects can lead to variations in the paper, even between two pages in the same ream.
At the point of use, these pages are loaded into a printer where they are stamped or dusted in toner and burned with lasers or sprayed with ink.
Any of these processes may alter the local texture or global topology of the sheet.
The pages may receive handwritten marks at any point before or after printing, and may subsequently be folded, creased, crumpled, flattened, burned, stained, soaked, or generally be subject to many other operations.
\emph{Augraphy}'s suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle.

@@

\emph{Augraphy} is a lightweight Python package for applying realistic perturbations to document images.
It is registered on the Python Package Index (PyPI) and can be installed using
\begin{center}
\textbf{\texttt{pip install augraphy}}
\end{center}
\emph{Augraphy} requires only a few other commonly-used Python scientific computing or image handling packages in order to run, such as NumPy \cite{numpy}. \emph{Augraphy} has been tested on Windows, Linux, and Mac computing environments. Listing \ref{lst:sample-code} shows how easy it is to get \emph{Augraphy} up and running to create a straightforward augmentation pipeline and apply it to an image:
%Examples of output generated by \emph{Augraphy} are shown in Figure~\ref{fig:augraphy_examples_3x5}.

\begin{lstlisting}[language=Python, label={lst:sample-code}, caption={Transforming an image with \emph{Augraphy}.}]
import augraphy; import cv2
pipeline = augraphy.default_augraphy_pipeline()
img = cv2.imread("image.png")
data = pipeline.augment(img)
augmented = data["output"]
\end{lstlisting}
Modern frameworks for machine learning like \emph{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the \emph{Augraphy} development team takes great pains to ensure our library's ease-of-use and compatibility.
%We wanted the library
The library is designed to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
The default \emph{Augraphy} pipeline (shown in the code snippet above) makes use of all of the augmentations available in \emph{Augraphy}, with starting parameters selected after manual visual inspection of several thousand images.

%We were unable to find any tools for producing training images of modern documents, in a way suitable for automated use. The Augraphy library is our attempt at filling this gap.\\

\emph{Augraphy} provides \numAugraphyAugmentations ~unique augmentations, which may be sequenced into a pipeline object that carries out the image manipulation.
Users of the library can define directed acyclic graphs of images and their transformations via the AugraphyPipeline API, representing the passage of a document through real-world alterations.
\emph{Augraphy} attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into three phases: ink, paper, and post.
The ink phase exists to sequence effects which specifically alter the printed ink --- like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time --- and transform them prior to ``printing".

@@

\begin{figure}
\centering
\scalebox{0.33}{
\includegraphics[]{figures/pipeline.png}}
\caption{Visualization of an Augraphy pipeline, showing the composition of several image augmentations together with a specific paper background} \label{fig:pipeline}
\end{figure}

@@

Augraphy provides \numAugraphyAugmentations ~out-of-the-box augmentations.
These augmentations are listed in Table~\ref{tab:augmentations}, and examples are shown in Figure~\ref{fig:augraphy-examples-github}.
As mentioned before, Ink Phase augmentations include those that imitate noisy processes that occur in a document's life cycle when ink is printed on paper.
These augmentations include \texttt{BleedThrough}, which imitates what happens when ink bleeds through from the opposite side of the page.
Another, \texttt{LowInkLines}, produces a streaking behavior common to printers running out of ink.

Augmentations provided by the Paper Phase include \texttt{BrightnessTexturize}, which introduces random noise in the brightness channel to emulate paper textures, and \texttt{Watermark}, which imitates watermarks in a piece of paper.
Finally, the Post Phase includes augmentations that imitate noisy-processes that occur after a document has been created.
These include \texttt{BadPhotoCopy}, which uses added noise to generate an effect of dirty copier, and \texttt{BookBinding}, which creates a book binding effect with shadow and curved lines to imitate how a page from a book might appear after being scanned with a flatbed scanner.
Other general-purpose augmentation libraries already exist for adding basic effects like blur, scaling, and rotation, but \emph{Augraphy} includes these types of augmentations as well.
Descriptions of- and motivation for each augmentation are available on GitHub. \footnote{\url{https://github.com/sparkfish/augraphy}}
% TODO: is there a more precise link for these descriptions?

%Augraphy is designed to replicate noise-like effects seen in real-world documents, and the library's
%, so each augmentation represents a feature that will appear in the final dataset.
%augmentations come in many flavors and types, varying not only in their visual effect but also in their software design.
%Other libraries already exist for adding basic effects like blur, scaling, and rotation; Augraphy includes augmentations for these as well. The more interesting effects come from a combination of primitive effects, and mimic document types out in the world.\\

% TODO: I don't think this table is entirely correct, some augmentations might be listed in the wrong columns
\begin{table}[]
    \centering
    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase.}
    \scalebox{0.81}{
    \begin{tabular}{lll}
    \toprule
        \textbf{Ink Phase} & \textbf{Paper Phase} & \textbf{Post Phase} \\
        \midrule
        \textsf{BleedThrough} & \textsf{BrightnessTexturize} & \textsf{BadPhotoCopy} \\
        \textsf{DirtyDrum} & \textsf{ColorPaper} & \textsf{BindingsAndFasteners} \\
        \textsf{DirtyRollers} & \textsf{Gamma} & \textsf{BookBinding} \\
        \textsf{Dithering} & \textsf{Geometric} & \textsf{Folding} \\
        \textsf{Faxify} & \textsf{LightingGradient} & \textsf{JPEG} \\
        \textsf{InkBleed} & \textsf{PageBorder} & \textsf{NoiseTexturize} \\
        \textsf{Letterpress} & \textsf{SubtleNoise} & \textsf{Watermark} \\
        \textsf{LowInkLine} & & \\
        \textsf{Markup} & & \\
        \textsf{PencilScribbles} & & \\
        \bottomrule
    \end{tabular}}
    \label{tab:augmentations}
\end{table}

\subsection{The Augraphy Library}
\emph{Augraphy} is a Python-based library, allowing for maximal accessibility for practitioners,
%The library was developed in Python, to allow maximal accessibility for practitioners,
and is designed with an object-oriented structure, with concerns divided across a class hierarchy.
When composed, different parts of the library interact to produce complex sequences of document image transformations, generating new synthetically-augmented document images.

%Modern frameworks for machine learning like \emph{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the \emph{Augraphy} development team takes great pains to ensure our library's ease-of-use and compatibility.
%We wanted the library to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
%The default Augraphy pipeline makes use of all of the augmentations available in \emph{Augraphy}, with starting parameters selected after manual visual inspection of several thousand images.
%Adding a diverse array of realistic features to documents can be done with the following five-line incantation:
%\begin{lstlisting}[language=Python]
%from augraphy import *
%pipeline = default_augraphy_pipeline()
%img = cv2.imread("image.png")
%data = pipeline.augment(img)
%augmented_img = data["output"]
%\end{lstlisting}

%\subsection{Base}
%\texttt{augraphy.base} is the core of the library, containing the central class for augmentations, another class for sequences of augmentations, and the pipeline class itself. The base classes exist to coordinate the compilation of discrete transformations into a larger pipeline, and to facilitate the operation and maintenance of these.\\

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\usepackage{booktabs}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{listings}
\usepackage{times}
\renewcommand{\floatpagefraction}{.8}
\usepackage{etoolbox}
\AtBeginEnvironment{quote}{\par\singlespacing\small}

@@

\newcommand{\numAugraphyAugmentations}{\emph{26}}
\newcommand{\numNoisyOfficeUNetEpochs}{\emph{426}}
\newcommand{\ocrCleanLevenshteinDistance}{\emph{TODO}}
\newcommand{\ocrAugraphyAverageLevenshteinDistance}{\emph{TODO}}

@@

\begin{abstract}
This paper introduces Augraphy, a Python library for constructing data augmentation pipelines for producing distortions commonly seen in real-world document image datasets.
Augraphy stands apart from other data augmentation tools by providing many different strategies to produce augmented versions of clean document images that appear as if they have been altered by standard office operations, such as printing, scanning, and faxing through old or dirty machines, degradation of ink over time, and handwritten markings.
This paper discusses the Augraphy tool, and shows how it can be used both as a data augmentation tool for (1) producing diverse training data for tasks such as document de-noising, and (2) generating challenging test data for evaluating model robustness on document image modeling tasks.

@@

\section{Introduction and Motivation}
Daily life in the modern world involves a plethora of tasks requiring the handling of unstructured data.
Often, this data is in the form of documents, which may appear very different from when they were originally produced, having been physically altered by printing, scanning, or photocopying processes.
Such real-world phenomena may introduce many types of distortions: for instance, folds, wrinkles, or tears in a page can cause color changes and shadows in a scanned document image; low or high printer ink settings may cause some regions of a document to be lighter or darker; and human-made annotations like highlighting or pencil marks can add noise to the page.

Many machine learning operations involving documents are impacted by the presence of noise, while high-level tasks like document classification and information extraction are frequently expected to perform well even on noisily-scanned document images.
For instance, the RVL-CDIP document classification corpus \cite{harley2015icdar-rvlcdip} consists of scanned document images, many of which have substantial amounts of scanner-induced noise, as does the FUNSD form understanding benchmark \cite{jaume2019-funsd}.
Other intermediate-level tasks like optical character recognition (OCR) and page layout analysis may perform optimally if noise in a document image is minimized \cite{character-recognition-systems,ogorman-document-image-analysis,Rotman2022-hh}.
The lower-level task of document de-noising tackles the document noise problem directly, by attempting to remove noise from a document image \cite{ref_noisyoffice,blind-denoising-iccv-2021,kulkarni-2020,patch-based-document-denoising,Mustafa_2018-wan}.
All of these tasks benefit from copious amounts of training data, and one way of generating large amounts of training data with noise-like artefacts is to use data augmentation.

@@

For this reason we introduce \emph{Augraphy}, an open-source Python-based data augmentation library for generating versions of document images that contain realistic noise artefacts commonly introduced via scanning, photocopying, and other office procedures.
\emph{Augraphy} differs from most image data augmentation tools by specifically targeting the types of alterations and degradations seen in document images.
\emph{Augraphy} offers \numAugraphyAugmentations ~individual augmentation methods out-of-the-box across three ``phases" of augmentations, and these individual phase augmentations can be composed together along with a ``paper factory" step where different paper backgrounds can be added to the augmented image.
The resulting document images are realistic, noisy versions of clean documents, as evidenced in Figure~\ref{fig:intro}, where we apply several \emph{Augraphy} augmentations to a clean document image in order to mimic the types of noise seen in a real-world noisy document image from RVL-CDIP.
This paper provides an overview of the \emph{Augraphy} library, and demonstrates how it can be used both as a training data augmentation tool and as an effective means for producing data for robustness testing.

\begin{table}[]
    \centering
    \caption{Comparison of various image-based data augmentation libraries. Number of augmentations is a rough count, and many augmentations in other tools are what Augraphy calls Utilities. Further, many single augmentations in Augraphy --- geometric transforms, for example --- are represented by multiple classes in other libraries.}
    \scalebox{0.9}{
    \begin{tabular}{lccccc}
    \toprule
        \textbf{Library} & \textbf{Num.} & \textbf{Document-} & \textbf{Pipeline-} & & \\
        \textbf{Name} & \textbf{Augmentations} & \textbf{Centric} & \textbf{Based} & \textbf{Python} & \textbf{License}  \\
    \midrule
        \emph{Augmentor} \cite{augmentor} & 27 & \xmark &  & \cmark & MIT \\
        \emph{Albumentations} \cite{ref_albumentations} & 216 & \xmark & \cmark & \cmark & MIT \\
        \emph{imgaug} \cite{ref_imgaug} & 168 & \xmark & \cmark & \cmark & MIT \\
        \emph{Augly} \cite{Papakipos2022-gq-augly} & 34 & \xmark & & \cmark & MIT \\
        \emph{DocCreator} \cite{ref_DocCreator} & 12 & \cmark & \xmark & \xmark & LGPL-3.0 \\
        \emph{Augraphy} (ours) & \numAugraphyAugmentations & \cmark & \cmark & \cmark & MIT\\
    \bottomrule
    \end{tabular}}
    \label{tab:augmentation-library-comparison}
\end{table}

\section{Related Work}

This section discusses prior work related to data augmentation and robustness testing, especially as it relates to document understanding and processing tasks.

\subsection{Data Augmentation}
A wide variety of data augmentation tools and pipelines exist for machine learning tasks, including  natural language processing (e.g., \cite{feng-etal-2021-survey,fadaee-etal-2017-data,wei-zou-2019-eda}), audio and speech processing (e.g., \cite{ko15_interspeech,audiogmenter,audio-framework}), and computer vision and image processing.
In the latter realm, popular tools include \emph{Augly} \cite{Papakipos2022-gq-augly}, \emph{Augmentor} \cite{augmentor}, \emph{Albumentations} \cite{ref_albumentations}, \emph{DocCreator} \cite{ref_DocCreator}, and \emph{imgaug} \cite{ref_imgaug}.
Augmentation strategies from these image-centric libraries are typically general-purpose, and include transformations like rotations, warps, and color modifications.
Table~\ref{tab:augmentation-library-comparison} compares \emph{Augraphy} with other image augmentation libraries and tools.
As can be seen, these other data augmentation libraries do not specifically provide support for imitating the corruptions commonly seen in document analysis corpora.

A notable exception to this is the \emph{DocCreator} image synthesizing tool \cite{ref_DocCreator}, which is targeted towards creating synthetic images that mimic common corruptions seen in document collections.
\emph{DocCreator} differs from \emph{Augraphy} in several crucial ways.
The first difference is that \emph{DocCreator}'s augmentations are meant to imitate those seen in historical (e.g., ancient or medieval) documents, while \emph{Augraphy} is intended to replicate noise caused by office room procedures.
\emph{DocCreator} was also written in the C++ programming language as a monolithic what-you-see-is-what-you-get tool, and does not have a scripting or API interface to enable use in a broader machine learning pipeline.
\emph{Augraphy}, in contrast, is written in Python and can be easily integrated into machine learning model development and evaluation pipelines, alongside other Python packages like PyTorch \cite{ref_PyTorch}.

@@

The introduction of noise-like corruptions and other modifications to image data can be used as a way of estimating and evaluating model robustness.
Prior work in this space includes the use of image blurring, contrast and brightness changes, color alterations, partial occlusions, geometric transformations, pixel-level noise (e.g., salt-and-pepper noise, impulse noise, etc.), and compression artefacts (e.g., JPEG) to evaluate image classification and object detection models (e.g., \cite{image-quality-impact,imagenet-c,pathology-recommendations,Hosseini2017-kn-google-api,face-recognition-impact,pathology-schomig,Vasiljevic2016-al-bluring-impact}).
More specific to the document understanding field, recent prior work has used basic noise-like corruptions to evaluate the robustness of document classifiers trained on RVL-CDIP \cite{saifullah-2022}.
Our paper also uses robustness testing as a way to showcase the effectiveness of \emph{Augraphy}, but rather than general image modifications like those described above, we use document-centric modifications to produce human-readable distortions which challenge OCR models.

\section{Document Distortion, Theory \& Technique}
Many approaches exist for adding features to an image, and many types of feature can be generated. The most common types of features added are Gaussian noise, blurring, geometric transformations like scaling, rotating, translating, and cropping, downsampling, font weighting, and so on.\\

These types of feature are certainly useful in general image analysis and understanding, but bear little relation to the types of features commonly found in real-world documents.

A sheet of paper out in the world begins its life as wood pulp, bleached, drained, and pressed flat by a long series of rollers. These are cut to size and stacked, then bound in reams and sent out for sale and use. This is the last time the sheet is clean in its useful lifetime, and even at this point, manufacturing defects can lead to variations in the paper, even between two pages in the same ream. At the point of use, these pages are loaded into a printer where they are stamped or dusted in toner and burned with lasers or sprayed with ink. Any of these processes may alter the local texture or global topology of the sheet. The pages may receive handwritten marks at any point before or after printing, and may subsequently be folded, creased, crumpled, flattened, burned, stained, soaked, or generally be subject to any of a million other operations. Any secretary can describe hundreds of different document distortion features; any schoolteacher, thousands.\\

Augraphy's suite of augmentations was designed to faithfully reproduce this level of complexity in the document lifecycle. Every feature just listed already has a direct implementation either within the library or on the development roadmap, with many more planned.\\

Some techniques exist for introducing these features into images of documents, including but not limited to the following:
\begin{enumerate}
\item Text can be generated independently of the paper texture, and can be overlaid onto the "paper" by a number of blending functions, allowing a variety of paper textures to be used. The NoisyOffice team did this.
\item Similarly, any markup features may be generated and overlaid by the same methods.
\item Documents can be digitized with a commercial scanner, or converted to a continuous analog signal and back with a fax machine.
\item The finished document image can be used as a texture and attached to a 3D mesh, then projected back to 2 dimensions to simulate physical deformation. DocCreator has a function to do this.
\end{enumerate}

Augraphy already has a story for the first three, with the fourth in planning.

\section{Augraphy}
This section dives into detail about the \emph{Augraphy} library.
We first provide a high-level overview of the library, then discuss the various augmentations supported out-of-the-box, and finally discuss details of the structure of the library.

@@

\emph{Augraphy} is a lightweight Python package for applying realistic perturbations to document images.
It is registered on the Python Package Index (PyPI) and can be installed using
\begin{center}
\textbf{\texttt{pip install augraphy}}
\end{center}
\emph{Augraphy} requires only a few other commonly-used Python scientific computing or image handling packages in order to run, such as NumPy \cite{numpy}. \emph{Augraphy} has been tested on Windows, Linux, and Mac computing environments and supports several recent major versions of Python 3. Listing \ref{lst:sample-code} shows how easy it is to get \emph{Augraphy} up and running to create a straightforward augmentation pipeline and apply it to an image:

\begin{lstlisting}[language=Python, label={lst:sample-code}, caption={Transforming an image with \emph{Augraphy}.}]
import augraphy; import cv2
pipeline = augraphy.default_augraphy_pipeline()
img = cv2.imread("image.png")
data = pipeline.augment(img)
augmented_img = data["output"]
\end{lstlisting}
Modern frameworks for machine learning like \emph{fastai} \cite{ref_fastai} aim to simplify the data handling requirements, and concordantly, the \emph{Augraphy} development team takes great pains to ensure our library's ease-of-use and compatibility.

\emph{Augraphy} is designed to be immediately useful with little effort, especially as part of a preprocessing step for training machine learning models, so great care was taken to establish good defaults.
The default \emph{Augraphy} pipeline (shown in the code snippet above) makes use of all of the augmentations available in \emph{Augraphy}, with starting parameters selected after manual visual inspection of several thousand images.

\emph{Augraphy} provides \numAugraphyAugmentations ~unique augmentations, which may be sequenced into pipeline objects which carry out the image manipulation.
Users of the library can define directed acyclic graphs of images and their transformations via the AugraphyPipeline API, representing the passage of a document through real-world alterations.
\begin{figure}
\centering
\scalebox{0.33}{
\includegraphics[]{figures/pipeline.png}}
\caption{Visualization of an Augraphy pipeline, showing the composition of several image augmentations together with a specific paper background} \label{fig:pipeline}
\end{figure}

\emph{Augraphy} attempts to decompose the lifetime of features accumulating in a document by separating the pipeline into three phases: ink, paper, and post.
The ink phase exists to sequence effects which specifically alter the printed ink --- like bleedthrough from too much ink on page, extraneous lines or regions from a mechanically faulty printer, or fading over time --- and transform them prior to ``printing".

@@

@@

Augraphy provides \numAugraphyAugmentations ~out-of-the-box augmentations.
These augmentations are listed in Table~\ref{tab:augmentations}.
As mentioned before, Ink Phase augmentations include those that imitate noisy processes that occur in a document's life cycle when ink is printed on paper.
These augmentations include \texttt{BleedThrough}, which imitates what happens when ink bleeds through from the opposite side of the page.
Another, \texttt{LowInkLines}, produces a streaking behavior common to printers running out of ink.

Augmentations provided by the Paper Phase include \texttt{BrightnessTexturize}, which introduces random noise in the brightness channel to emulate paper textures, and \texttt{Watermark}, which imitates watermarks in a piece of paper.
Finally, the Post Phase includes augmentations that imitate noisy-processes that occur after a document has been created.
These include \texttt{BadPhotoCopy}, which uses added noise to generate an effect of dirty copier, and \texttt{BookBinding}, which creates an effect with shadow and curved lines to imitate how a page from a book might appear after capture by a flatbed scanner.

Other general-purpose augmentation libraries already exist for adding basic effects like blur, scaling, and rotation, but \emph{Augraphy} includes these types of augmentations for completeness and utility.
Descriptions of each augmentation are available online, along with the motivation for their development. \footnote{\url{https://augraphy.readthedocs.io/en/latest/}}

\begin{table}[]
    \centering
    \caption{Individual \emph{Augraphy} augmentations for each augmentation phase, in suggested position within the pipeline. Augmentations that work well in more than one phase are listed in the last column.}
    \scalebox{0.81}{
    \begin{tabular}{llll}
    \toprule
        \textbf{Ink Phase} & \textbf{Paper Phase} & \textbf{Post Phase} & \textbf{Multiple} \\
        \midrule
        \textsf{BleedThrough} &  \textsf{ColorPaper}& \textsf{BadPhotoCopy} & \textsf{BrightnessTexturize} \\
        \textsf{LowInkLines} & \textsf{Watermark} & \textsf{BindingsAndFasteners} & \textsf{DirtyDrum} \\
        \textsf{InkBleed} & \textsf{Gamma} & \textsf{BookBinding} & \textsf{DirtyRollers} \\
        \textsf{Letterpress} & \textsf{LightingGradient} & \textsf{Folding} & \textsf{Dithering} \\
        & \textsf{SubtleNoise} & \textsf{JPEG} & \textsf{Geometric}\\
        & & \textsf{Markup} & \textsf{NoiseTexturize}\\
        & & \textsf{Faxify} & \textsf{PencilScribbles}\\
        & & \textsf{PageBorder} & \\
        \bottomrule
    \end{tabular}}
    \label{tab:augmentations}
\end{table}

\subsection{The Augraphy Library}
\emph{Augraphy} is a Python-based library, allowing for maximal accessibility for practitioners, and is designed with an object-oriented structure, with concerns divided across a class hierarchy.
When composed, augmentations from the library interact to produce complex document image transformations, generating realistic new synthetically-augmented document images.

There are four ``main sequence" classes in the \emph{Augraphy} codebase, which together provide the bulk of the library's functionality.

We now discuss each of these:

\smallskip
\noindent\textbf{\texttt{Augmentation}.} ~The \texttt{Augmentation} class is the most basic class in the project, and essentially exists as a thin wrapper over a probability value in the interval [0,1].
Every augmentation contained in a pipeline has its own chance of being applied during that pipeline's execution.

\smallskip
\noindent\textbf{\texttt{AugmentationResult}.} ~After an augmentation is applied, the output of its execution is stored in an \texttt{AugmentationResult} object and passed forward through the pipeline.
These objects also record a full copy of the augmentation runtime data, as well as any metadata that might be relevant for debugging or other advanced use.

\smallskip
\noindent\textbf{\texttt{AugmentationSequence}.} ~A list of \texttt{Augmentation}s --- together with the intent to apply those Augmentations in sequence --- determines an \texttt{AugmentationSequence}, which is itself both an \texttt{Augmentation} and callable.
In practice, these are the model for the pipeline phases discussed previously; they are essentially lists of \texttt{Augmentation} constructor calls which produce callable \texttt{Augmentation} objects of the various flavors explored in \texttt{AugmentationSequences} are applied to the image during each of the \texttt{AugmentationPipeline} phases, and in each case yield the image, transformed by some of the Augmentations in the sequence.

\smallskip
\noindent\textbf{\texttt{AugmentationPipeline}.} ~The bulk of the heavy lifting in \emph{Augraphy} resides in the Augmentation pipeline, which is our abstraction over one or more events in a physical document's life.

Consider the following sequence of events:
\begin{quote}
The initial printing of the document when ink adhered to the paper material, or several weeks later when the document was adhered to a public board, annotated, defaced, and torn away from its securing staples.
Fifty years later, our protagonist page resurfaces in the library archive during routine preservation-scanning efforts. Conservationists use delicate tools to gently position and record an image of the document, storing this in a public repository.
\end{quote}
An \texttt{AugmentationPipeline} can model this entire sequence of events, or any individual event within.
